---
title: "Functions"
description: |
  A quick tutorial on functions and creating custom functions
author:
  - name: Jenn Lewis
    url: https://github.com/15jennlee15
date: 06-03-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(rio)
library(here)

data <- import(here("data", "movie_metadata.csv_movie_metadata.csv"))

data <- data %>%
  mutate(gross = as.numeric(gross),
         budget = as.numeric(budget),
         profit = gross-budget)
```
###Introduction

In this blog tutorial we will be learning about creating functions in R. To follow along in RStudio you will need the following packages installed and loaded:

-tidyverse
-rio
-here

Furthermore, you will want to download and import the dataset we use here from this site:
https://data.world/popculture/imdb-5000-movie-dataset

Make sure you put this data in your working directory, or I'd recommend making a new R project and adding a data folder there!

Description of data:
28 variables for 5043 movies and 4906 posters, spanning across 100 years in 66 countries. There are 2399 unique director names, and thousands of actors/actresses. Examples of variables in the data set are: "movie_title"  "title_year"  "movie_facebook_likes"

###What's a Function?

What is a function? Very simply, a function is a block of reusable code that is used to perform an action.  
In R, we can store a function as an object and thus be able to recall the function repeatedly and perform an operation (or several) very quickly and easily with a single command.  Let's break it down a little bit more.

Here's an example of a function
```{r Example Function}

mean_function <- function(variable) {
  mean(variable)
}

```
First by using the "<-" we are assigning the function to an object name.  Note that the name of the function is meaningful, that is, we can guess what it does by it's name. This is important as if you create a lot of functions, you may loose track of the purpose of each, furthermore, it helps make your code more readable to others.

Our example function is very simple, it calculates the mean of a variable.  Now, we could just do this with mean(variable), but I wanted to use a simple example for our first function.

Next, a function is composed of three parts:

1) *Body*: this is the code inside the function (inside the curly brackets {})
    In our example, the 'body' is the part within the curly brackets, in this case:  mean(variable)
    
2) *Formals*: these are the arguements supplied to the function - controls how we can call the function
    In our example, the formal, the arguement we supply to the function, is 'variable'. The formals are listed in the     parantheses right after function.  Your function can have multiple formals. 
    
   So for example, let's say we wanted to have a function that calculates the mean of two variables.  In this           case, we'd need to provide two formals, variable 1 and variable 2 (see example below).  Note that you can call the    formals whatever you want. In this case we used 'variable1' and 'variable2'. We could have also used 'x' and 'y',    'cat' and 'dog', anything really. The names are arbitrary, but it is most helpful to give the formals names that     are meaninful so you can remember what type of information you need to provide it. 
    
```{r Second Example Function with Two Formals}
mean_function2 <- function(variable1, variable2) {
  (variable1 + variable2)/2
}
```


3) *Environment*:  the "map" of the location of the function's variables - where it lives

