---
title: "Functions"
description: |
  A quick tutorial on functions and creating custom functions
author:
  - name: Jenn Lewis
    url: https://github.com/15jennlee15
date: 06-03-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(rio)
library(here)

data <- import(here("data", "movie_metadata.csv_movie_metadata.csv"))

data <- data %>%
  mutate(gross = as.numeric(gross),
         budget = as.numeric(budget),
         profit = gross-budget)
```
### Introduction

In this blog tutorial we will be learning about creating functions in R. To follow along in RStudio you will need the following packages installed and loaded:

-tidyverse

-rio

-here

Furthermore, you will want to download and import the dataset we use here from this site:
https://data.world/popculture/imdb-5000-movie-dataset

Make sure you put this data in your working directory, or I'd recommend making a new R project and adding a data folder there!

Description of data:
28 variables for 5043 movies and 4906 posters, spanning across 100 years in 66 countries. There are 2399 unique director names, and thousands of actors/actresses. Examples of variables in the data set are: "movie_title"  "title_year"  "movie_facebook_likes"

### What's a Function?

What is a function? Very simply, a function is a block of reusable code that is used to perform an action.  
In R, we can store a function as an object and thus be able to recall the function repeatedly and perform an operation (or several) very quickly and easily with a single command.  Let's break it down a little bit more.

Here's an example of a function

```{r Example Function, echo=TRUE}
mean_function <- function(variable) {
  mean(variable)
}

```
First by using the "<-" we are assigning the function to an object name.  Note that the name of the function is meaningful, that is, we can guess what it does by it's name. This is important as if you create a lot of functions, you may loose track of the purpose of each, furthermore, it helps make your code more readable to others.

Our example function is very simple, it calculates the mean of a variable.  Now, we could just do this with mean(variable), but I wanted to use a simple example for our first function. The input to this function would be a variable, the output would be the mean of that variable.  You can test this example function by entering different variables from our dataset.

Next, a function is composed of three parts:

1) *Body*: this is the code inside the function (inside the curly brackets {})
    In our example, the 'body' is the part within the curly brackets, in this case:  mean(variable)
    
2) *Formals*: these are the arguements supplied to the function - controls how we can call the function
    In our example, the formal, the arguement we supply to the function, is 'variable'. The formals are listed in       the parantheses right after function.  Your function can have multiple formals. 
    
   So for example, let's say we wanted to have a function that calculates the mean of two variables.  In this           case, we'd need to provide two formals, variable 1 and variable 2 (see example below).  Note that you can call      the formals whatever you want. In this case we used 'variable1' and 'variable2'. We could have also used 'x' and     'y', 'cat' and 'dog', anything really. The names are arbitrary, but it is most helpful to give the formals names     that are meaninful so you can remember what type of information you need to provide it. 
    
```{r Second Example Function with Two Formals, echo=TRUE}
mean_function2 <- function(variable1, variable2) {
  (mean(variable1) + mean(variable2))/2
}
```
3) *Environment*:  the "map" of the location of the function's variables - where it lives. How the function finds       the values assoiciated with the names.  While you explicitly state the body and formals, the environment is         implicitly specified based on where the function was defined.

Let's try out our functions using our movie dataset (link to download above) which I named 'data'. First let's try out the 'mean_function'.  You can supply the function with a variable and it should output the mean. Let's try it out.

```{r Trying Functions Out, echo =TRUE}
#Here's our function
mean_function <- function(variable) {
  mean(variable)
}

#What is the average imdb score for the films in our dataset?
mean_function(data$imdb_score)
```
We called the function using the name we assigned it, supplied the input(our variable), and received the output (our mean) of 6.44!

Hooray!

Let's try another.  Let's find out what the average film duration is.

```{r Tryout Functions Number 2, echo=TRUE, error=TRUE}
mean_function(data$duration)

```
Uh oh! Our result was NA? Why do you think that happened?

When we look at our dataframe, we see that the variable 'duration' does have missing data.  We need to remove that to get our function to work.  To do that, let's just add it to our function!

```{r Function Remove missing Data, echo=TRUE}
#Let's write over our previous 'mean_function' to remove missing data so it works on more of our variables
mean_function <- function(variable) {
  mean(variable, na.rm=TRUE)
}

#Now let's try to find out the average film duration again
mean_function(data$duration)
```
Great it worked!  The average film duration is 107 minutes.

Now let's try out our second function. Let's combine the number of facebook likes for actor1 and actor2 and see what the overall average is. But first, let's modify the function to remove missing data.

```{r Testing Out Function 2 Average Number of Facebook Likes}
#modify the function to exclude missing data
mean_function2 <- function(variable1, variable2) {
  (mean(variable1, na.rm=TRUE) + mean(variable2, na.rm=TRUE))/2
}

#Remember we have to provide two variables for our second function
mean_function2(data$actor_1_facebook_likes, data$actor_2_facebook_likes)

```
The average number of facebook likes is 4,105! Great job!

### Custom Functions

Now that you have some basic function knowledge, let's take a try at creating some more complex functions.  Let's first try to make a function that is very specific to this dataset.  Let's try something fun.  Let's write a function that will tell us the average imdb score for a given actor!

```{r Custom Function 1, echo=TRUE}
#We first want to pick a meaningful name for our function, so it is clear what it does.  Also what's the arguements we need to provide to the function?  The actor's name right?  So we'll have one formal for this function.
average_imdb <- function(actor) {
  #Now the dataset in it's current form isn't ideal for this question, but luckily we can change the dataset within   the function.  Notice that nothing is saved to our global environment when we do this, it remains in the function.
  
  #There are three columns of actors in the dataset - actor1, 2, and 3.  We will want to gather these all into one      column first. I also used select here to select just the relevant variables
  df <- data %>%
    select(actor_1_name, actor_2_name, actor_3_name, imdb_score) %>%
    gather(number, actor, -imdb_score )
  #Next, we want to aggregate the data such that when there are multiple instances of an actor, we calculate their overall mean
    df <- aggregate(imdb_score ~ actor, df, mean)
 #Next, so that we can call up the actor, we give the rows names of the actors.
  row.names(df) <- df$actor 
 #Lastly, we call up the imdb score for the given actor
 df[actor,"imdb_score"]
    }

#And that's our function. So you can see it more clearly, here it is written out without the comments:
average_imdb <- function(actor) {
  df <- data %>%
    select(actor_1_name, actor_2_name, actor_3_name, imdb_score) %>%
    gather(number, actor, -imdb_score )
  
  df <- aggregate(imdb_score ~ actor, df, mean)
  row.names(df) <- df$actor 
  
 df[actor,"imdb_score"]
    }

```

Now let's try the function out!

```{r Trying out Actor Function, echo=TRUE}

average_imdb("Tom Cruise")
average_imdb("Johnny Depp")
average_imdb("Will Smith")

```

Great! This worked, it reported the average imdb for each actor input we gave it.  

Now, what if I misspelled an actor's name, what would the function to then?  Let's try it.

```{r Misspelled Name, echo=TRUE, error=TRUE}

average_imdb("tom cruz")
```
The function returned 'NA'.  This makes sense given that there isn't a 'tom cruz' in our list, but that may not be clear to the user of our function.  One thing we can do to make our function even more effective, is to add helpful error messages. Let's try adding a more descriptive error message to our average imdb function.

```{r Helpful Error Messages, eval=TRUE}
average_imdb <- function(actor) {
  df <- data %>%
    select(actor_1_name, actor_2_name, actor_3_name, imdb_score) %>%
    gather(number, actor, -imdb_score )
  
  df <- aggregate(imdb_score ~ actor, df, mean)
  row.names(df) <- df$actor 
  
 name <- df[actor,"imdb_score"]
 
 if(is.na(name)) {
    return("This actor is not in our database.  Did you check your spelling?  Make sure to capitalize the first letter of the first and last name")
 }
 else {
   return(name)
 }

}

average_imdb("Tom Crude")

```

```{r Custom Function 2}
#Create a custom function that will pull out descriptive statistics for a variable

descriptives <- function(x) {
  data.frame(mean(x), sd(x), min(x), max(x), length(x))
  }

#Test if it works
descriptives(data$imdb_score)
```

Additional Resources on Functions:

https://adv-r.hadley.nz/functions.html#function-fundamentals

https://swcarpentry.github.io/r-novice-inflammation/02-func-R/

