---
title: "Functions"
description: |
  A quick tutorial on functions and creating custom functions
author:
  - name: Jenn Lewis
    url: https://github.com/15jennlee15
date: 06-03-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(rio)
library(here)

data <- import(here("data", "movie_metadata.csv_movie_metadata.csv"))

data <- data %>%
  mutate(gross = as.numeric(gross),
         budget = as.numeric(budget),
         profit = gross-budget)
```
###Introduction

In this blog tutorial we will be learning about creating functions in R. To follow along in RStudio you will need the following packages installed and loaded:

-tidyverse
-rio
-here

Furthermore, you will want to download and import the dataset we use here from this site:
https://data.world/popculture/imdb-5000-movie-dataset

Make sure you put this data in your working directory, or I'd recommend making a new R project and adding a data folder there!

Description of data:
28 variables for 5043 movies and 4906 posters, spanning across 100 years in 66 countries. There are 2399 unique director names, and thousands of actors/actresses. Examples of variables in the data set are: "movie_title"  "title_year"  "movie_facebook_likes"

###What's a Function?

What is a function? Very simply, a function is a block of reusable code that is used to perform an action.  
In R, we can store a function as an object and thus be able to recall the function repeatedly and perform an operation (or several) very quickly and easily with a single command.  Let's break it down a little bit more.

Here's an example of a function
```{r Example Function}

mean_function <- function(variable) {
  mean(variable)
}

```
A function is composed of three parts:

1) Body: this is the code inside the function (inside the curly brackets {})
2) Formals: these are the arguements supplied to the function - controls how we can call the function
3) Environemnt:  the "map" of the location of the function's variables - where it lives

