---
title: "Looping through with purrr::map"
description: |
  In this tutorial we'll learn how to use map to avoid repetitive code and loop through lists to extract elements or run regressions
author:
  - name: Tamara Niella
    url: https://www.linkedin.com/in/tniella 
date: 06-09-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, include = FALSE}
library(tidyverse)
library(rio)
library(here)
library(stringr)
#install.packages("splitstackshape")
library(splitstackshape)
library(magrittr)
library(glue)

options(scipen=999)

data <- import(here("data", "movie_metadata.csv_movie_metadata.csv"))

data <- data %>%
  mutate(gross = as.numeric(gross),
         budget = as.numeric(budget),
         profit = gross-budget)
```

```{r Custom Function 1}
#Make a function that tells you the average imdb rating for a specfic actor; this function will only work within this data set

average_imdb <- function(x) {
 df <- aggregate(imdb_score ~ actor_1_name, data, mean)
 
 row.names(df) <- df$actor_1_name 
 
 df[x,"imdb_score"]
    }

#Test function, provide actor name in quotes to get their average imdb_score

average_imdb("Tom Cruise")
average_imdb("Johnny Depp")
average_imdb("Will Smith")

```

```{r Custom Function 2}
#Create a custom function that will pull out descriptive statistics for a variable

descriptives <- function(x) {
  data.frame(mean(x), sd(x), min(x), max(x), length(x))
  }

#Test if it works
descriptives(data$imdb_score)
```

```{r}

# let's nest our data by genre

df_genre <- data %>% 
  drop_na()%>%
  group_by(genres)%>%
  nest()

# let's nest our data by country 

df_country <- data %>% 
  drop_na() %>%
  group_by(country)%>%
  nest()

# Country seems to be a more reasonable grouping variable to work with - In genres there seems to be a lot of combinations of different genres. but let's take a look at the number of observations per group for the two different categories 

save_map <- map(df_country$data, ~length(.x[[1]]))
save_map2 <- map(df_genre$data, ~length(.x[[1]]))
```

For both categories there seems to be a very uneven number of observations per group. However, in genres this might be due to the fact that there are a lot of combinations. I am going to go ahead and use a criteria to determine the genre of the movie as the first genre that appears in the combination, and then I will nest the data again according to this new criteria (I will consider the other genres within the same genre as "sub-genres")

```{r}
#let's separate the combination of genres for each movie and keep the first genre as main genre in a new variable

data_new <- data%>%
 drop_na() %>%
 filter(movie_facebook_likes != "0")


data_new<- cSplit(data_new, "genres", "|")

data_new %<>% rename(main_genre = genres_1)

#now let's nest data by main genre 

df_main_genre <- data_new%>%
 select(-genres_2, -genres_3, -genres_4, -genres_5, -genres_6, -genres_7, -genres_8) %>%
 filter(!grepl('Thriller|Western|Musical|Family|Romance|Sci-Fi', main_genre)) %>%
# need to remove thriller, western, musical, family, romance, sci_fi for having less than 5 movies
 group_by(main_genre) %>%
 nest()


```

You'll see in the code above that we used `grepl` when filtering. `grepl` is a base function that looks for patterns in data that is supplied to it, typically outputting a logical vector of `TRUE` and `FALSE`. However, when used in association with `filter`, `grepl` tells filter to look for patterns in (or to exclude in our case) whatever is supplied in the first argument - six genres for us - out of the second argument, the supplied data. In our example, it is looking for any of the genres supplied and is excluding them. `grepl` is helpful when we have so many different things we are telling `filter` to look for, as it helps exclude repetitive code when filter (e.g., filter != 'Thriller`| filter != 'Western' and so on).

Now let's map through the list to run a regression predicting profit from number of facebook likes for the movie 

```{r}
df_mg_nonull <- df_main_genre[[2]]
df_mg_nonull <- df_mg_nonull[!map_lgl(df_mg_nonull, is.null)]

map(df_mg_nonull, ~lm(profit~movie_facebook_likes, .x))

#but actually, I think it might be better if I bouild that data fram as a list of lists 

#season to wave 
df_mg_list <- data_new %>%
 select(-genres_2, -genres_3, -genres_4, -genres_5, -genres_6, -genres_7, -genres_8)%>%
 mutate(main_genre = as.factor(main_genre)) %>%
 filter(!grepl('Thriller|Western|Musical|Family|Romance|Sci-Fi', main_genre)) %>%
 droplevels(data_new$main_genre) %>%
# need to remove thriller, western, musical, family, romance, sci_fi for having less than 5 movies
   as_tibble()


by_main_genre <- split(df_mg_list, df_mg_list$main_genre)


model <- map(by_main_genre, ~lm(profit ~ movie_facebook_likes, .x))

#model

coefs <- map(model, ~coef(.x))

slopes <- map_dbl(coefs, 2)



# I think splitting works better for this then nesting, but I'm leaving both methods for now, and then wecan decide if we want to keep one or the other or both 

```

