---
title: "Making and Saving Plots"
description: |
 This is a tutorial about making and saving plots using parallel iterations
author:
  - name: Karlena Ochoa 
    url: https://example.com/norajones
date: 06-03-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r include = FALSE, setup }
library(tidyverse)
library(rio)
library(here)
library(stringr)
#install.packages("splitstackshape")
library(splitstackshape)
library(magrittr)
library(glue)

options(scipen=999)

data <- import(here("data", "movie_metadata.csv_movie_metadata.csv"))

data <- data %>%
  mutate(gross = as.numeric(gross),
         budget = as.numeric(budget),
         profit = gross-budget)
```

```{r include = FALSE}
#Make a function that tells you the average imdb rating for a specfic actor; this function will only work within this data set

average_imdb <- function(x) {
 df <- aggregate(imdb_score ~ actor_1_name, data, mean)
 
 row.names(df) <- df$actor_1_name 
 
 df[x,"imdb_score"]
    }

#Test function, provide actor name in quotes to get their average imdb_score

average_imdb("Tom Cruise")
average_imdb("Johnny Depp")
average_imdb("Will Smith")

```

```{r include = FALSE}
#Create a custom function that will pull out descriptive statistics for a variable

descriptives <- function(x) {
  data.frame(mean(x), sd(x), min(x), max(x), length(x))
  }

#Test if it works
descriptives(data$imdb_score)
```

```{r include = FALSE}

# let's nest our data by genre

df_genre <- data %>% 
  drop_na()%>%
  group_by(genres)%>%
  nest()

# let's nest our data by country 

df_country <- data %>% 
  drop_na() %>%
  group_by(country)%>%
  nest()

# Country seems to be a more reasonable grouping variable to work with - In genres there seems to be a lot of combinations of different genres. but let's take a look at the number of observations per group for the two different categories 

save_map <- map(df_country$data, ~length(.x[[1]]))
save_map2 <- map(df_genre$data, ~length(.x[[1]]))
```


```{r include = FALSE}
#let's separate the combination of genres for each movie and keep the first genre as main genre in a new variable

data_new <- data%>%
 drop_na() %>%
 filter(movie_facebook_likes != "0")


data_new<- cSplit(data_new, "genres", "|")

data_new %<>% rename(main_genre = genres_1)

#now let's nest data by main genre 

df_main_genre <- data_new%>%
 select(-genres_2, -genres_3, -genres_4, -genres_5, -genres_6, -genres_7, -genres_8) %>%
 filter(!grepl('Thriller|Western|Musical|Family|Romance|Sci-Fi', main_genre)) %>%
# need to remove thriller, western, musical, family, romance, sci_fi for having less than 5 movies
 group_by(main_genre) %>%
 nest()


```


```{r include = FALSE}
df_mg_nonull <- df_main_genre[[2]]
df_mg_nonull <- df_mg_nonull[!map_lgl(df_mg_nonull, is.null)]

map(df_mg_nonull, ~lm(profit~movie_facebook_likes, .x))

#but actually, I think it might be better if I bouild that data fram as a list of lists 

#season to wave 
df_mg_list <- data_new %>%
 select(-genres_2, -genres_3, -genres_4, -genres_5, -genres_6, -genres_7, -genres_8)%>%
 mutate(main_genre = as.factor(main_genre)) %>%
 filter(!grepl('Thriller|Western|Musical|Family|Romance|Sci-Fi', main_genre)) %>%
 droplevels(data_new$main_genre) %>%
# need to remove thriller, western, musical, family, romance, sci_fi for having less than 5 movies
   as_tibble()


by_main_genre <- split(df_mg_list, df_mg_list$main_genre)


model <- map(by_main_genre, ~lm(profit ~ movie_facebook_likes, .x))

#model

coefs <- map(model, ~coef(.x))

slopes <- map_dbl(coefs, 2)



# I think splitting works better for this then nesting, but I'm leaving both methods for now, and then wecan decide if we want to keep one or the other or both 

```



```{r include = FALSE}
# As seen above, you can use map to extract the coefficients separately, but what if we wanted to do that AND extract the ses all at once? That's where map2 comes in!

# compare model 1 vs model 2, model 2 adds a second predictor (imbd score) to see if there is a better fit
## this is just showing the second model as an example for the tutorial

model2 <- map(by_main_genre, ~lm(profit ~ movie_facebook_likes + imdb_score, .x))

# Get our two models into a tibble that we can then compare the models and plot
model_comparison_df <- by_main_genre %>% 
  bind_rows(.id = "genre") %>% #for tutorial, make note on what this does and why you have to do it to use group-by
  group_by(genre) %>% 
  na.omit() %>% 
  nest() %>% 
  mutate(m1 = map(data, ~lm(profit ~ movie_facebook_likes, .x)),
         m2 = map(data, ~lm(profit ~ movie_facebook_likes + imdb_score, .x)))
  

model_comparison_df$m1[[1]]

#model comparison 
compare_modelfit <- anova(model_comparison_df$m1[[1]], model_comparison_df$m2[[1]])

# putting the model comparison into a dataset that has extracted the p-value
## This is where you use map2 to loop through each of the model lists and compare them with Anova
compare_all <- model_comparison_df %>%
    mutate(anova_output = map2(m1, m2, anova),
           p_val = map_dbl(anova_output, list("Pr(>F)", 2)))

# tidying the data so that we have the models in long-format and extracting r-square for each model as its own column
compare_all_tidy <- compare_all %>% 
  gather(model, output, m1:m2) %>% 
  mutate(r_square = map_dbl(output, ~summary(.x)$r.squared))

```

Now that we have our data in tidy format we can plot the r-square for each model by Genre. We use model (model 1 and 2) as our x-axis and r-square on the y-axis. We can use facet-wrap to create a plot for each genre side by side. We aren't going to worry about making it look pretty right now, we just want to get an idea of what it looks like. For example, it looks like our model fits well for Animation and Documentaries, but not so well for Action, Comedy, Crime. 

```{r making rsquare plots, echo = TRUE}
#show r-square for both models in one plot for all genres
rsquare_plots <- compare_all_tidy %>%  
ggplot(aes(model, r_square)) +
    geom_col(aes(fill = model)) +
    facet_wrap(~genre) +
    guides(fill = "none") +
    scale_fill_brewer(palette = "Set2")

rsquare_plots

```

Now say that we are interested in seeing the coefficients plotted for each model we can use `gather`, `select`, `mutate`, and `unnest` to get it in the format we need for plotting. We use `unnest` at the end to get the data out of the list column format. 
  
```{r making coefs plots, include = FALSE, echo = TRUE}
#unnest and tidy to be able to plot coefs
coefs_plot <- model_comparison_df %>%
    gather(model, output, m1:m2) %>%
    mutate(tidied = map(output, broom::tidy)) %>% 
    select(genre, model, tidied) %>%
    unnest()

#get movies names for plots 
to_plot_coefs <- names(coef(model_comparison_df$m1[[1]])) 

#plot all genres together
ploting_df_coefs <- coefs_plot %>%
    filter(term %in% to_plot_coefs) %>%
ggplot(aes(estimate, term, color = model)) +
    geom_point() +
    scale_color_brewer(palette = "Set1") +
    facet_wrap(~genre) +
  theme_minimal() +
  labs(x = "Coefficient",
       title = "Plot of coefficients for Number of Facebook Likes and IMDB Score Predicting Movie Profit",
       subtitle = "Displayed by Genre")

ploting_df_coefs
```

Ultimately, we decide we want to look at model fit for the two different models, model 1 looking at Facebook likes predicting profit and model 2 looking at Facebook likes and IMDB score predicting profit. We will use `pmap` to prepare the data. 

In order to use pmap to get a separate plot for each genre, we will need to group by Genre and then nest. This will give us two columns - the first genre, and then all the data in a list column called data. This is where we will being pulling information in order to plot them. 

We will us pmap because it will allow us to loop through two or more vectors. This is similiar to map2, which we learned in a previous tutorial can loop through two vectors, but pmap has the flexibility to loop through more than two vectors. In this case we will only be looping through 2, but if we decided to loop through 3 we could add a label for each of the plots. When using pmap you need to first say what the list is; in our case we will put pmap(list(data, genre). Now that they are in a list we can refer to them in their position. For example, data can be referred to as ..1 and genre will be ..2. In order to create each plot we will use mutate and save it to "plot". From there we just use ggplot like we regularly would. We will put ..1 as our data input because that says pull from the data list column. 

```{r making and saving plots, echo = TRUE}

#plot genres separately

#group by genre and nest to be able to use pmap    
for_plotting <- coefs_plot %>% 
    bind_rows(.id = "id") %>% 
    group_by(genre) %>% 
    nest()


#make all plots using pmap 
profit_by_genre <- for_plotting %>% 
    mutate(plot = pmap(list(data, genre),
    ~ggplot(..1, aes(term, estimate, color = model)) +
    geom_point(size = 3) +
    scale_color_brewer(palette = "Set1", name = "Model", labels = c("1", "2")) +
    theme_minimal() +
    labs(x = "Coefficient",
         y = "Profit in Dollars",
       title =  glue("Model fit for predicting profit for {..2} movies")) +
      scale_x_discrete(labels = c("Intercept", "IMDB Score", "Facebook"))))
    

#We want to test a few to make sure they are working properly. 
#If we type profit_by_genre it wouldn't automatically display all the plots,
#we have to use indexing to call them. 

#It's always important to test a few plots to make sure they look right. 
profit_by_genre$plot[[1]]
profit_by_genre$plot[[5]]
profit_by_genre$plot[[6]]

```

In order to save the plots we need to create a directory. We are going to make a folder called "plots" with a subfolder called "profit_by_genre" 

Create directory (folder) for plots

`fs::dir_create(here::here("plots", "profit_by_genre"))`

Then we will name all the plots and make sure all the titles are in the same format. We will call them by their genre. 

`files <- str_replace_all(tolower(profit_by_genre$genre), " ", "-")`
`paths <- here::here("plots", "profit_by_genre", glue("{files}.png"))`

You can check the paths that you created to make sure they are there.
You do this by just calling `paths`. 

We will use walk2, which is also a parallel iteration, to save the plots to that folder we created. Walk2 is different than other parallel iterations because we are using it for the side effects and not necessarily the value like we do for map2. This is helpful in cases you may want to make a lot of plots and save them to a disk. 

`walk2(paths, profit_by_genre$plot, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)`


*Thanks for following along, we hope you enjoyed our tutorial! *



